Exploring dimensions of biodiversity in Japanese ferns

### 2021-07-08 ms/SI.Rmd
Switch to kableExtra for tables
still need to format column names properly

```{r setup-si, include = FALSE, cache = FALSE}
# Load functions only used when rendering Rmds
source(here::here("R/ms_functions.R"), local = TRUE)
# Set knitr options
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, results = "hide", cache = FALSE)
```

@@

```{r load-data-si, cache = FALSE}
library(flextable)
library(ftExtra)

tar_load(c(
  "japan_shp",
  "comm_scaled_list",
  "occ_point_data_ferns",
  "biodiv_ferns_spatial",
  "biodiv_ferns_endemic_spatial",
  "k_taxonomy",
  "k_phylogeny",
  "traits_nmds",
  "ppgi",
  "phy_sig_results",
  "binary_sig_results",
  "lrt_results"
))
```

@@

```{r phy-sig, results = "as-is"}
phy_sig_results %>%
  mutate(across(c(kval, lambda, k_pval, lambda_pval), ~format(., digits = 2))) %>%
  rename(
    ` ` = trait,
    `*K*` = kval,
    `λ` = lambda,
    `*p* (*K*)` = k_pval,
    `*p* (λ)` = lambda_pval,
    `*n*` = n
    ) %>%
  as_flextable() %>%
  autofit() %>%
  colformat_md(part = "all")
```

@@

```{r phy-sig-binary, results = "as-is"}
binary_sig_results %>%
  select(trait, D, num_present, num_absent, prob_random, prob_brownian) %>%
  arrange(trait) %>%
  mutate(across(c(D, prob_random, prob_brownian), ~format(., digits = 2))) %>%
  rename(
    ` ` = trait,
    `*n* (present)` = num_present,
    `*n* (absent)` = num_absent,
    `*p* (random)` = prob_random,
    `*p* (Brownian)` = prob_brownian
    ) %>%
  as_flextable() %>%
  fontsize(size = 7, part = "all") %>%
  autofit() %>% 
  colformat_md(part = "all")
```

@@

```{r lrt-null, results = "as-is"}
lrt_results %>%
  filter(comparison == "null_model") %>%
  select(-null_formula, -comparison) %>%
  tidyr::extract(full_formula, "model_type", "~ ([^ ]+) ") %>%
  rename_resp_vars %>%
  rename_model_type %>%
  select(model_type, resp_var, chi2_LR, df, loglik_null, loglik_full, p_value) %>%
  arrange(model_type, resp_var) %>%
  mutate(across(where(is.double), ~format(., digits = 2))) %>%
  # colformat_md() doesn't work on grouped tables
  # group_by(model_type) %>%
  # as_flextable(hide_grouplabel = TRUE) %>%
  rename(
    Response = resp_var,
    `Model type` = model_type,
    `χ^2^` = chi2_LR,
    `logL (full model)` = loglik_full,
    `logL (null model)` = loglik_null,
    `*p*` = p_value
  ) %>%
  as_flextable %>%
  merge_v(j = "Model type") %>% 
  valign(valign = "top") %>% 
  fontsize(size = 7, part = "all") %>%
  autofit() %>%
  colformat_md(part = "all")
```

>>>>

```{r setup-si, include = FALSE, cache = FALSE}
# Load functions only used when rendering Rmds
source(here::here("R/ms_functions.R"), local = TRUE)
# Set knitr options
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, results = "hide", cache = FALSE)

# Load packages only used when knitting Rmd
library(kableExtra)
```

@@

```{r load-data-si, cache = FALSE}
tar_load(c(
  "japan_shp",
  "comm_scaled_list",
  "occ_point_data_ferns",
  "biodiv_ferns_spatial",
  "biodiv_ferns_endemic_spatial",
  "k_taxonomy",
  "k_phylogeny",
  "traits_nmds",
  "ppgi",
  "phy_sig_results",
  "binary_sig_results",
  "lrt_results"
))
```

@@

```{r phy-sig, results = "as-is"}
phy_sig_results %>%
  mutate(across(c(kval, lambda, k_pval, lambda_pval), ~format(., digits = 2))) %>%
  kbl(booktabs = TRUE) %>%
  kable_styling(latex_options = "striped")
```

@@

```{r phy-sig-binary, results = "as-is"}
binary_sig_results %>%
  select(trait, D, num_present, num_absent, prob_random, prob_brownian) %>%
  arrange(trait) %>%
  mutate(across(c(D, prob_random, prob_brownian), ~format(., digits = 2))) %>%
  kbl(booktabs = TRUE) %>%
  kable_styling(latex_options = c("striped", "scale_down"))
```

@@

```{r lrt-null, results = "as-is"}
lrt_table_data <-
lrt_results %>%
  filter(comparison == "null_model") %>%
  select(-null_formula, -comparison) %>%
  tidyr::extract(full_formula, "model_type", "~ ([^ ]+) ") %>%
  rename_resp_vars %>%
  rename_model_type %>%
  select(model_type, resp_var, chi2_LR, df, loglik_null, loglik_full, p_value) %>%
  arrange(model_type, resp_var) %>%
  mutate(across(where(is.double), ~format(., digits = 2)))

lrt_table_data %>%
  select(-model_type) %>%
  kbl(
    col.names = colnames(.) %>% str_replace_all("resp_var", ""),
    booktabs = TRUE) %>%
  pack_rows(index = base::table(lrt_table_data$model_type)) %>%
  kable_styling(latex_options = "striped")
```
